Dynein project log

### 2016-09-06 thesis_stuff/thesis_stuff.tex
Add notes on annual review paper.

\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\pagestyle{fancy}
\fancyhf{}
% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example footer:
%\rfoot{\color{headings} {\sffamily Last update: \today}. Typeset with Xe\LaTeX}

@@

A $\sigma = \sqrt{\frac{1}{n<W>}}$ does not make sense. For one, $\sqrt{<\Delta x>}$ should be in the numerator, since it is the
single-timestep standard deviation. Plus it seems like for longer times the distribution would get more spread out, not less, hence
$\sqrt{n}$ should be in the numerator as well? But the CLT says it should be in the denominator...

\section{Biochemistry Papers}

@@

\subsection{Physical Parameters from Winch Model paper}
Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm, $L_t = 14$nm, binding angle: 34 degrees from vertical, motor
domain radius: 7nm, motor domain angle from vertical: 30 degrees, tail angle: 0 degrees between linkers when poststroke, 40 degrees when prestroke.

\section{Citations}
\subsection{Annual Review, 8-state Mechanochemical diagram}
Cianfrocco, M*., DeSantis, M*., Leschziner, A., Reck-Peterson, S. ``Mechanism and Regulation of Cytoplasmic Dynein'' \textit{Annu. Rev. Cell. Dev. Biol.} 2015: 31:83-108.\\

Goes over in detail the various steps of the Dynein chemical cycle. Links to a lot of good papers.\\

\subsection{Weihong's Dynein stepping data}
Qiu, W., Derr, N., Goodman, B., Villa, E., Wu, D., Shih, W., Reck-Pterson, S. ``Dynein achieves processive motion using both stochastic and coordinated stepping.'' \textit{Nature Structural & Molecular Biology}. 2012, 19:193-200.\\

>>>>

\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\pagestyle{fancy}
\fancyhf{}
% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example footer:
%\rfoot{\color{headings} {\sffamily Last update: \today}. Typeset with Xe\LaTeX}

@@

A $\sigma = \sqrt{\frac{1}{n<W>}}$ does not make sense. For one, $\sqrt{<\Delta x>}$ should be in the numerator, since it is the
single-timestep standard deviation. Plus it seems like for longer times the distribution would get more spread out, not less, hence
$\sqrt{n}$ should be in the numerator as well? But the CLT says it should be in the denominator...\\
\\
\section{Papers}

@@

\textbf{Physical Parameters from Winch Model paper}:\\
Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm, $L_t = 14$nm, binding angle: 34 degrees from vertical, motor
domain radius: 7nm, motor domain angle from vertical: 30 degrees, tail angle: 0 degrees between linkers when poststroke, 40 degrees when prestroke.

\subsection{Annual Review, 8-state Mechanochemical diagram}
Cianfrocco, M*., DeSantis, M*., Leschziner, A., Reck-Peterson, S. ``Mechanism and Regulation of Cytoplasmic Dynein'' \textit{Annu. Rev. Cell. Dev. Biol.} 2015: 31:83-108.\\

Goes over in detail the various steps of the Dynein chemical cycle. Eight-state model as follows:\\

\begin{enumerate}
\item Dynein begins cycle with AAA1 binding site open.
\item ATP then binds to the AAA1 binding site.
\item ATP binding causes ``ring closure,'' where the AAA1 and AAA2 subdomains shift closer together.
\item Ring closure (ie ATP binding) causes the buttress to shift, causing the MTBD to lose MT affinity.
\item Ring closure (ATP binding) also causes the linker to bend 90 degrees, causing the monomer to enter the pre-powerstroke state. The order of states 4. and 5. is unknown, but entering pre-powerstroke \textit{after} unbinding from the MT causes more directional motion. The role of ATP hydrolysis also is not understood as of this paper (2015).
\item Random walk of the low-MT-affinity MTBD eventually leads to weak rebinding at a new place on the MT.
\item Rebinding causes a change in the MTBD back to its high affinity state. AAA4 moves to prevent steric clash when the linker straightens. AAA5/6 move away from AAA1 and the linker straightens to its post-powerstroke conformation. NOTE: this is distinct from the conformation in steps 1-4 in that AAA1/2 is still closed.
\item The linker shifts some more and AAA1/2 opens up, releasing ADP.
\end{enumerate}

\subsection{Weihong's Dynein stepping data}
Qiu, W., Derr, N., Goodman, B., Villa, E., Wu, D., Shih, W., Reck-Pterson, S. ``Dynein achieves processive motion using both stochastic and coordinated stepping.'' \textit{Nature Structural \& Molecular Biology}. 2012, 19:193-200.\\
